Analytical choices for analyzing multidimensional behavior - many analyst test hypotheses about human speech.

### 2020-10-31 RR_manuscript/Draft_RR.Rmd
added method section

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.

>>>>

# Methods (mostly copy-paste from Evo-RR)
This project involves a series of steps (X-X) that begin recruiting independent groups of scientists to analyze the data, continuing through allowing the scientists to analyze the data as they see fit, generating peer review ratings of the analyses (based on methods, not results), evaluating the variation in effects among the different analyses, and producing the final manuscript. We estimate that this process, from the time of an in-principle acceptance of this stage 1 Registered Report, will take XX months (Table X). The factor most likely to delay our timeline is the rate of completion of the original set of analyses by independent groups of scientists.

## Step 1: Recruitment and Initial Survey of Analysts
Initiating authors (SC, JC, TR) created a publicly available document providing a general description of the project (LINK) and a short prerecorded slide show that summarizes the study and research question (LINK). The project will be advertised via Social Media, using mailing lists for linguistic and psychological societies (full scope of these lists is not fixed but will include LIST OF LISTS), and via word of mouth. The target population is active speech science researchers with a graduate degree (or currently studying for a graduate degree) in a relevant discipline. Researchers can choose to work independently or in a small team. For the sake of simplicity, we refer to single researcher or small teams as ‘analysis teams’.

Recruitment for this project is ongoing but we aim for a minimum of XX analysis teams independently evaluating each dataset (see sample size justification below). We will simultaneously recruit volunteers to peer-review the analyses conducted by the other volunteers through the same channels. Our goal is to recruit a similar number of peer-reviewers and analysts, and to ask each peer reviewer to review a minimum of four analyses. If we are unable to recruit at least half the number of reviewers as analysis teams, we will ask analysts to serve also as reviewers (after they have completed their analyses). All analysts and reviewers will share co-authorship on this manuscript and will participate in the collaborative process of producing the final manuscript. All analysts will sign a consent (ethics) document (LINK).

## Step 2: Primary Data Analyses
Analysis teams will register and answer a demographic and expertise survey (LINK). We will then provide them with the acoustic data set and request that they answer the following research question: RESEARCH QUESTION HERE. Once their analysis is complete, they will answer a structured survey (LINK), providing analysis technique, explanations of their analytical choices, quantitative results, and a statement describing their conclusions. They will also upload their analysis files (including the additionally derived data and text files that were used to extract and preprocess the acoustic data), their analysis code [if applicable], and a detailed journal-ready statistical methods section.

## Step 3: Peer Reviews of Analyses (DO WE STILL DO THIS? CAN'T REMEMBER)
At a minimum, each analysis will be evaluated by four different reviewers, and each volunteer peer-reviewer will be randomly assigned methods sections from at least four analyst teams (the exact number will depend on the number of analysis teams and peer reviewers recruited). Each peer reviewer will register and answer a demographic and expertise survey identical to that asked of the analysts. Reviewers will evaluate the methods of each of their assigned analyses one at a time in a sequence determined by the initiating authors (SC, JC, TR). The sequences will be systematically assigned so that, if possible, each analysis is allocated to each position in the sequence for at least one reviewer. For instance, if each reviewer is assigned four analyses to review, then each analysis will be the first analysis assigned to at least one reviewer, the second analysis assigned to another reviewer, the third analysis assigned to yet another reviewer, and the fourth analysis assigned to a fourth reviewer. Balancing the order in which reviewers see the analyses controls for order effects, e.g. a reviewer might be less critical of the first methods section they read than the last.

The process for a single reviewer will be as follows. First, the reviewer will receive a description of the methods of a single analysis. This will include the narrative methods section, the analysis team’s answers to our survey questions regarding their methods, including analysis code, and the data set. The reviewer will then be asked, in an online survey (LINK), to rate both the acoustic analysis and the statistical analysis on a scale of 0-100 based on these prompts:

“Rate the overall appropriateness of the acoustic analysis to answer the research question with the available data. To help you calibrate your rating, please consider the following guidelines:

100. A perfect analysis with no conceivable improvements from the reviewer
 75. An imperfect analysis but the needed changes are unlikely to dramatically alter final interpretation
 50. A flawed analysis likely to produce either an unreliable estimate of the relationship or an over-precise estimate of uncertainty
 25. A flawed analysis likely to produce an unreliable estimate of the relationship and an over-precise estimate of uncertainty
 0. A dangerously misleading analysis, certain to produce both an estimate that is wrong and a substantially over-precise estimate of uncertainty that places undue confidence in the incorrect estimate.

*Please note that these values are meant to calibrate your ratings. We welcome ratings of any number between 0 and 100."

After providing this rating, the reviewer will be presented with this prompt, in multiple-choice format: “Would the analytical methods presented produce an analysis that is (a) publishable as is, (b) publishable with minor revision, (c) publishable with major revision, (d) deeply flawed and unpublishable?” The reviewer will then be provided with a series of text boxes and the following prompts: 
“Please explain your ratings of this analysis.
Please evaluate the selection of acoustic features.
Please evaluate the operationalization of acoustic features.
Please evaluate the choice of statistical analysis type.
Please evaluate the process of choosing variables for and structuring the statistical model.
Please evaluate the suitability of the variables included in (or excluded from) the statistical model.
Please evaluate the suitability of the structure of the statistical model.
Please evaluate choices to exclude or not exclude subsets of the data.
Please evaluate any choices to transform data (or, if there were no transformations, but you think there should have been, please discuss that choice).”

After submitting this review, a methods section from a second analysis will then be made available to the reviewer. This same sequence will be followed until all analyses allocated to a given reviewer have been provided and reviewed. After providing the final review, the reviewer will be simultaneously provided with all four (or more) methods sections that reviewer has just completed reviewing, the option to revise their original ratings, and a text box to provide an explanation. The invitation to revise the original ratings will be as follows: “If, now that you have seen all the analyses you are reviewing, you wish to revise your ratings of any of these analyses, you may do so now.” The text box will be prefaced with this prompt: “Please explain your choice to revise (or not to revise) your ratings.”

## Step 4: Evaluate Variation
Initiating authors (SC, JC, TR) will conduct the analyses outlined in this section. We will describe the variation in model specification in several ways. First, we will calculate summary statistics describing variation among analysis, including the nature and number of acoustic measures, the operationalization and the temporal domain of measurement, the nature and number of variables per model included as fixed effects, the nature and number of interaction terms, the nature and number of random effects [if applicable], as well as the mean, standard deviation and range of effect sizes reported.

We will summarize the variability in standardized effect sizes and predicted values of dependent variables among the individual analyses using standard random effects meta-analytic techniques. We anticipate that the majority of statistical analyses will be expressible as a (generalized) linear regression model.

ADD FORMULA

SHOULD WE TRANSFORM ALL MODELS AS BAYESIAN MODELS TO QUANTIFY THE EFFECT SIZE AS A PROB DISTRIBUTION? IF SO NEED TO DESCRIBE HOW.

TR:TRUE?

First, we will derive standardized effect sizes from each individual analysis. Since researchers are likely using multi-level linear regression models, common effect size measures such as Cohen's d are inappropriate. In multi-level models the variance components are partitioned into multiple sources of variation (e.g. varying intercept of speakers and items, varying by-predictor slopes, etc.). We thus will take into account all of the variance sources of the models (Hedges, 2007) and derive the index $\delta_t$ (where the t stands for “total” variance), which is calculated by the estimated difference between group means ($\beta$), divided by the square root of the sum of all variance components like so:

$$\delta_t = \frac{\beta}{\sqrt{\sum_{i=1}^{n} \sigma^2_{i}}}$$
Where $_i$ refers to the individual variance components.

CHECK IF THIS IS CORRECTLY EXPRESSED, NOT SURE ABOUT THE SUM SIGN...

Variation in the resulting effect sizes can be due to many different sources, one of which is the model architecture and the specification of random effect structure. Hypothetically, two analyst teams can arrive at two different effect sizes, even if they have made the exact same measurement, processed the data in the exact same way, and used the same predictor combination, but, crucially, differ in their random effect structure (e.g. one team assumes random intercepts only, the other team uses random slopes). Thus, additionally, we will run all analyses with a prespecified maximal random effect structure for all predictors.

TR: THIS HAS SOME PRACTICAL ISSUES, NEED TO DISCUSS

WRITE ABOUT HOW TO HANDLE GAMS

...

## Step 6: Facilitated Discussion and Collaborative Write-Up of Manuscript
Analysts and initiating authors will discuss the limitations, results, and implications of the study and collaborate on writing the final manuscript for review as a stage-2 Registered Report.
